---
title: "Fast Car App"
author: "Mark Nicholls"
date: "16/07/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(GGally)
data("mtcars")
theme_set(theme_light())
```

## Fast Car App

This is a presentation about my app submission for the Data Products Course project.  

I have made an app that will predict the standing quarter mile time of a car, the model is trained on the MTcars data set.

The model is built from the following 3 features

- Weight (wt)
- Horsepower (hp)
- Number of Cylinders (cyl)

## Weight Relationship

```{r echo=FALSE, message=FALSE, warning=FALSE}
mtcars %>% 
  ggplot(aes(qsec, wt)) + 
  geom_line() + 
  geom_smooth(method = "lm") +
  labs(
    title = "Relationship Weight to Quarter Mile time",
    y = "Weight (1000s lb)",
    x = "Quarter Mile Time (seconds)"
  )

```

## Horsepower Relationship

```{r echo=FALSE, message=FALSE, warning=FALSE}
mtcars %>% 
  ggplot(aes(qsec, hp)) + 
  geom_line() + 
  geom_smooth(method = "lm") +
  labs(
    title = "Relationship Horsepower to Quarter Mile time",
    y = "Horsepower",
    x = "Quarter Mile Time (seconds)"
  )

```

## Cylinder Relationship

```{r echo=FALSE, message=FALSE, warning=FALSE}
mtcars %>% 
  ggplot(aes(qsec, factor(cyl), group = cyl)) + 
  geom_boxplot() + 
  coord_flip() +
  labs(
    title = "Relationship Cylinder to Quarter Mile time",
    y = "Cylinders",
    x = "Quarter Mile Time (seconds)"
  )

```

